Methods paper for erosion

### 2017-08-16 docs/methods/erosion_methods.tex
made a few small changes to the methods paper

For the shear stress and the pressure, we will use odd-even integration
which achieves spectral accuracy if the integrand is no stronger than
$\mathcal{O}(\rho^{-1})$.  Since both these integrands are too strong,
the singularity must be weakened.  This can be done by adding a constant
density function which has no effect on the shear stress and
pressure~\cite{}.  In particular, the shear stress due to the
double-layer potential is equivalent to
\begin{align}
  \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      \ssigma(\yy) \, ds_{\yy} \\ 
      &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
\end{align}
For the pressure, the double-layer potential is equivalent to
\begin{align}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation} 
All the layer potentials are compatible with a fast summation such as
the Fast Multipole Method (FMM).  The majority of the

>>>>

For the shear stress and the pressure, we will use odd-even integration
which achieves spectral accuracy if the integrand is no stronger than
$\mathcal{O}(\rho^{-1})$.  Since both these integrands are too strong,
the singularity must be weakened.  This can be done by adding a constant
density function which has no effect on the shear stress and
pressure~\cite{poz1992}.  In particular, the shear stress due to the
double-layer potential is equivalent to
\begin{align}
  \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      \ssigma(\yy) \, ds_{\yy} \\ 
      &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
\end{align}
For the pressure, the double-layer potential is equivalent to
\begin{align}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\Gamma} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation} 
The majority of the computational cost comes from evaluating the the
double-layer potential $\mathcal{D}$ in equation~\eqref{eqn:DLP}.  This
layer potential can be efficiently evaluated using a fast summation
method such as the Fast Multipole Method
(FMM)~\cite{gre-rok1987}\footnote{The FMM for the Stokes double-layer
poetntial was supplied by Manas Rachh.}.  By using the
FMM,~\eqref{eqn:completed_DLP} can be solved with $\mathcal{O}(N)$
operations, where $N$ is the total number of discretization points.

In our erosion model, the shear stress must be computed which requires
evaulating the layer potential~\eqref{eqn:shearStressDLP}.  In our
implementation, this calculation is done directly which requires
$\mathcal{O}(N^2)$ operations.  This complexity could be reduced with
the kernel-independent FMM~\cite{yin-bir-zor2004}.  However, since this
calculation is only computed once per time step, unlike the velocity
double-layer potential that must be evaluated at each GMRES iteration.
